Structured Versus Decorated Cospans

### 2020-11-17 cospans.tex
Update cospans.tex

@@

@@

@@

>>>>

and then the image of this 2-morphism under the double functor $\lH$ is given by:

@@

On the other hand, applying the double functor $\lH$ first gives:

@@

This double functor $\lH$ satisfies the equations $S \lH_1 = HS$ and $T \lH_1=HT$.

@@

where $$d \maps 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{d_1 \times d_2} F(c_1) \times F(c_2) \xrightarrow{\phi_{c_1,c_2}} F(c_1+c_2) \xrightarrow{F(j)}F(c_1 +_b c_2).$$ The image of this horizontal 1-cell is then given by $\lH(M \odot N)$:
